---
title: "Assignment 1 - Blackpoll Warbler"
author: "Jill Hunt"
date: '2018-02-27'
output: html_document
---
##Loaded tidyverse and lubridate packages
```{r}

library(tidyverse)
library(lubridate)

```

##Read in datafile
```{r}

blpw.all <- readRDS("~/Desktop/r4ds/blpw.all.RDS")

```

##Check status of columns
```{r}

sapply(blpw.all, class)

```

##Change year and month to intergers
```{r}

blpw.all$year<-as.integer(blpw.all$year)
blpw.all$month<-as.integer(blpw.all$month)

```

##Combine year, month and day into one column (separated by a dash)
```{r}

blpw.all$date <- with(blpw.all, ymd(paste(year,month,day,sep = "-")))

```

##Grouped by band number, arranged it by band and date, created column for the first mass relative to the recapture mass
```{r}

blpw.band <- blpw.all %>%
  group_by(band) %>%
  arrange(band,date) %>%
  mutate(diff_mass=mass-first(mass)) %>% data.frame()

```

##Since we're looking for "Time of Year" as opposed to specific "Year", we can make all years 0. So create another column ("date") where the year was all changed to 0000
```{r}

blpw.band2 <- blpw.band %>% 
  mutate(date = make_date(!year,month,day))

```

##Since we're observing the change in mass, we only need data for birds that have been recaptured. So filter "recap" column to only have recaptured birds (R)
```{r}

blpw.band3 <- filter(blpw.band2, recap == 'R')

```

##Created ggplot using filtered dataset
```{r}

ggplot(data = blpw.band3, mapping = aes(x = date, y = diff_mass, colour = band))+
  geom_point()+
  geom_line()+
  facet_wrap(~location, nrow = 1)+
  theme(legend.position = 'none')+
  ylab("Mass (in grams, relative to capture date)")+
  xlab("Time of Year")

```

